On the marginal value of swimming in woodland caribou

### 2021-06-07 paper/manuscript.Rmd
minor edits to paper

Our focus on forage is due to the limited presence of predators in our system. Throughout their range, wolves (*Canis lupus*) are the primary predator of caribou. Because there are no wolves on the Island of Newfoundland, coyotes (*Canis latrans*) and black bears (*Ursus americanus*) are the majors predator of caribou (Lewis and Mahoney 2014). Within the Fogo Island archipelago there are no black bears and coyotes exist at low density (Huang et al. 2021), while the probability of coyote occurrence decreases on the smaller islands. The low density of predators throughout the archipelago is therefore an unlikely driver of swimming in our system, though predation may still influence swimming behaviour for caribou elsewhere in their range (e.g. Jeffery et al. 2007).

@@

Swimming behavior was common among GPS radio-collared caribou in the population (n = 29, for collaring details see Peignier et al. 2019). We identified `r nevents` swimming events over three years (Figure 2). In total, 13 of 29 collared female caribou swam among islands (Figure 2). Of the caribou that swam, caribou swam on average approximately `r neventidMedian` (range = `r neventidMin`-` neventidMax`) times per year and remained on each island for a median of `r dur` (range =  `r durMin`-`r durMax`) days before swimming again. We found that caribou residency increased proportionally with the size of the island for islands larger than approximately 0.1 km^2, such that caribou spent less time on smaller islands and more time on larger islands, providing preliminary evidence for links between forage limitation and the marginal value theorem (Figure 2B). In many cases, the smaller islands in the archipelago are forage limited and the larger islands provide greater opportunities to forage.

>>>>

Our focus on forage is due to the limited presence of predators in our system. Throughout their range, wolves (*Canis lupus*) are the primary predator of caribou. Because there are no wolves on the Island of Newfoundland, coyotes (*Canis latrans*) and black bears (*Ursus americanus*) are the majors predator of caribou (Lewis and Mahoney 2014). Within the Fogo Island archipelago there are no black bears; the density of coyotes is low (Huang et al. 2021) and the probability of coyote occurrence decreases on the smaller islands. The low density of predators throughout the archipelago is therefore an unlikely driver of swimming in our system, though predation may still influence swimming behaviour for caribou elsewhere in their range (e.g. Jeffery et al. 2007).

@@

We identified `r nevents` swimming events over three years (Figure 2). In total, 13 of 29 collared female caribou swam among islands (Figure 2). Of the caribou that swam, caribou swam on average approximately `r neventidMedian` (range = `r neventidMin`-` neventidMax`) times per year and remained on each island for a median of `r dur` (range =  `r durMin`-`r durMax`) days before swimming again. We found that caribou residency increased proportionally with the size of the island for islands larger than approximately 0.1 km^2, such that caribou spent less time on smaller islands and more time on larger islands, providing preliminary evidence for links between forage limitation and the marginal value theorem (Figure 2B). In many cases, the smaller islands in the archipelago are forage limited and the larger islands provide greater opportunities to forage.
